### 2015-09-14 vmcai-2016-tex/summary-heap.tex
Fixed a few things to be consistent

\section{A Symbolic Heap}
A \emph{symbolic heap}, as defined in this work, is a tuple
$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map}
$\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment}
$\eta$ are partial functions, and the~\emph{path condition} $\phi$ is
a predicate over the program variables. Given reference $r$ in the heap,
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
associated with $r$. The constraint associated with each
location is a guard representing the conditions under which the
associated reference maps to the given location. By definition, any
location appears at most once in any given value set. Unions of value
sets containing the same location are resolved by forming a
disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
location-field pair in the heap.

@@

For well-formed symbolic heaps, a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. Also, for a well-formed heap, all locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

\section{Operational Semantics}
This paper defines symbolic initialization using
a small-step operational semantics in the context of a syntactic machine with a CESK architecture~\cite{Felleisen:1992, saints-MS}. The
surface (input) syntax and machine (state) syntax (which omits the symbolic heap definition previously given and the environment) are shown
in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
are italicized. Ellipses indicate zero or more repetitions. Tuples
omit the commas for compactness.

@@

The machine state $\cfgnt{s}$ includes the program
registry $\mu$, the symbolic heap, the global path constraint, the environment $\eta$, the current expression (i.e., program), and the continuation $\cfgnt{k}$. The registry never changes so it is
omitted from the state tuple in the rest of the presentation. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation is used with symbolic heaps as well.

>>>>

\section{A Symbolic Heap}
A \emph{symbolic heap}, as defined in this work, is a pair
$(\cfgnt{L}\ \cfgnt{R})$, indicating a \emph{location map}
$\cfgnt{L}$ and a \emph{reference map} $\cfgnt{R}$.  Given a reference $r$ in the heap,
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
associated with $r$. The constraint associated with each
location is a guard representing the conditions under which the
associated reference maps to the given location. By definition, any
location appears at most once in any given value set. Unions of value
sets containing the same location are resolved by forming a
disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
location-field pair in the heap.

@@

A \emph{well-formed} symbolic heap is \emph{deterministic} and \emph{type consistent}. Determinism means a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$.
Type consistent means that all locations in a guarded value set from a reference have the same type\footnote{Although not treated in this presentation, the concept naturally extends to polymorphic languages}:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

\section{Operational Semantics}
This paper defines symbolic initialization using
a small-step operational semantics in the context of a syntactic machine with a CESK architecture~\cite{Felleisen:1992, saints-MS}. The
surface  syntax  (input) and machine  syntax (state) are shown
in~\figref{fig:syntax}. The machine syntax omits the list based syntactic structures for the partial functions in the heap etc.  Terminals are in bold face while non-terminals
are italicized. Ellipses indicate zero or more repetitions. Tuples
omit the commas for compactness.

@@

The machine state $\cfgnt{s}$ includes the program
registry $\mu$, the symbolic heap, the~\emph{path condition} $\phi$, the \emph{environment} $\eta$, the current expression (i.e., program), and the continuation $\cfgnt{k}$. The registry never changes so it is
omitted from the state tuple in the rest of the presentation. The path condition is a predicate of the program variables. 
The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation is used with symbolic heaps as well.
